### 2019-03-14 manuscript/discussion.tex
Small changes in the discussion, two final lines added

\subsection*{Disentangling trait interactions in the context of diversification} %RB: merged two titles; good?

@@

%B: yielding to %R here. I still think there is overwhelming support for this statement, and few of the cited papers show convincingly that, for example, diploidization happens within five orders of magnitude compared with polyploidization, rendering "relatively rare" obsolete or invalid. (P.S. Rare not the same as unimportant!)
%B: was: Diploidization is widely considered to be relatively rare, compared with polyploidization \citep{husband_2013}, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}.
Our exploratory analyses recover some support for inclusion of diploidization in the history of the family, but without significant effects on inferences of diversification dynamics.
The implications of the results of our diploidization analyses, as well as much of the other recent work on WGDs, are interesting because they conflict with other lines of evidence, especially those concerning the observed simple synteny of genomes in Solanaceae, and patterns of evolution as self-incompatibility loci.

Flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}. 
Following polyploidization, it is possible for genome reorganization, downsizing, and loss \citep{dodsworth_2015, zenil_2016, mandakova_2018}. %B: commas, etc.: importantly rm: "has been observed" this is _only_ true on very, very, short time scales
As a consequence, it is possible that nearly all extant species classified as ``diploid" in our analyses, based on cytogenetic data, are possibly secondary diploids, having undergone both polyploidization and re-diploidization.
Unduly ignoring secondary diploidization would necessarily underestimate the rate of transitions from polyploids to diploids.
It would then likely cause inflated net diversification rates for diploids, because species considered diploid may have been ancestrally polyploid, instead. %B: added before conflict/edits
We find strong support for including the diploidization rate parameter ($\delta$) in analyses that include only ploidy \cref{table:bayesfactors}. %B <- %Rosana, inspect this please. It's a merge of conflicted lines.
However, we find only modest support for diploidization in the joint model, and conclusions regarding the relative effects of ploidy and breeding system on diversification are robust to its inclusion.
Furthermore, estimating the rate of diploidization, based on our ploidy level classifications, is highly uncertain (see parameter $\delta$ in \cref{suppfigure:DP,suppfigure:DPAB,suppfigure:IDCDCP,suppfigure:IDCDCPAB}), and yields dramatic changes in ancestral reconstructions (\cref{suppfigure:DPnodipasr,suppfigure:DPasr,suppfigure:DPnodipABasr,suppfigure:DPABasr,suppfigure:IDCDCPnodipasr,suppfigure:IDCDCPasr,suppfigure:IDCDCPnodipABasr,suppfigure:IDCDCPABasr}).

@@

Regardless of whether genome polypoidization, followed by widespread diploidization, is a dominant mechanism of genome evolution in Solanaceae, it is clear that our present understanding of the evolution of ploidy and breeding systems is incomplete.
An increasingly forceful weight of evidence seems to support WGDs in the ancestry of many angiosperms. %cite
It is then easily inferred that many species have undergone diploidization, alongside genome size and chromosome number reductions. %cite
Inference of such a common genome upheaval in eudicot history seems to clash with the data indicating that a homologous mechanism of SI, which breaks down nearly invariably in natural and induced tetraploids \citep{stone_2002,mcclure_2009}, has been present continually in many families, including Solanaceae \citep{igic_2006}. 
Most problematically in this context, it is unclear how to explain the maintenance of trans-generic polymorphism at the orthologous S-loci in this and other families.
As well, chromosome numbers and genome comparisons within the family (esp. `x=12' clade, containing \textit{Solanum} and \textit{Nicotiana}) reveal strong conservation.
\citet{wu_2010a} review the evidence from map-based genome comparisons and find that tomato and potato differ six inversions, tomato and eggplant by 24 inversions and five translocations, tomato and pepper by 19 inversions and six translocations, and tomato and tobacco by ca. 10 inversions and 11 translocations (likely underestimated).
Recovery of such simple relationships would require outstanding convergent loss of duplicated segments.
In either case, all of the approaches make ample assumptions, and it seems that at least some of them will necessitate deep revisions.
Our study, for example, made numerous assumptions in coding trait states (e.g. what constitutes a polyploid or diploid, SI or SC species), in models used for analyses (e.g. irreversibility of SI loss underlain by trans-specific orthologous S-loci), and many more, which could each mislead inference. %B: -> %R: Rosana, take a look at this.
% no discussion of magnitude of \delta vs \rho!
% problems: this system has a big set of advantages - carefully curated (co-)occurrences of two traits, genetic basis, etc. and everything is still contradictory and opaque.

@@

Estimating rates of trait linked diversification models is not only a problem of difficult parametric inference (as disscussed in  \citet{rabosky_2010, beaulieu_2015}), but also, a problem of inadequate  ``*SSE'' model specification that can result in misleading inferences when the presence of a second trait has a complex interaction with the focus trait first used to model diversification. 
We presented a roadmap with a series of analyses that can identify whether unknown or unobservable traits are worth pursuing. 
In this roadmap, we have proposed fitting HiSSE models that have effectively shown that some binary states associated with diversification under BiSSE analyses are actually not different in net diversification terms, and instead a hidden state is linked to differences in the diversification rate \citep{beaulieu_2016}.  
If that is the case on a system, raising the question of the identity of the hidden state should be considered as the next step in the modeling process. 
When considering  a second candidate trait, one can model the complex interactions via a MuSSE model, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
Since MuSSE might also suffer from hight type I errors considering more heterogeneity using a hidden state model on top of the multistate SSE is necessary to adequately infer the effect of the complex interactions in the speciation and extinction process.

>>>>

\subsection*{Disentangling trait interactions in the context of diversification} %RB: merged two titles; good? % R-Good

@@

%B: yielding to %R here. I still think there is overwhelming support for this statement, and few of the cited papers show convincingly that, for example, diploidization happens within five orders of magnitude compared with polyploidization, rendering "relatively rare" obsolete or invalid. (P.S. Rare not the same as unimportant!)
%B: was: Diploidization is widely considered to be relatively rare, compared with polyploidization \citep{husband_2013}, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}.
%Our exploratory analyses recover some support for inclusion of diploidization in the history of the family, but without significant effects on inferences of diversification dynamics.
%R- The line above is included in the bottom so no more need for that here
The implications of the results of our diploidization analyses, as well as much of the other recent work on WGDs, are interesting because they conflict with other lines of evidence, especially those concerning the observed simple synteny of genomes in Solanaceae, and patterns of evolution as self-incompatibility loci.

Flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}. 
Following polyploidization, it is possible for genome reorganization, downsizing, and loss to occur \citep{dodsworth_2015, zenil_2016, mandakova_2018}. %B: commas, etc.: importantly rm: "has been observed" this is _only_ true on very, very, short time scales
As a consequence, nearly all extant species classified as ``diploid" in our analyses, based on cytogenetic data, are possibly secondary diploids, having undergone both polyploidization and re-diploidization.
Unduly ignoring secondary diploidization would necessarily underestimate the rate of transitions from polyploids to diploids.
It would then likely cause inflated net diversification rates for diploids, because species considered diploid may have been ancestrally polyploid, instead. %B: added before conflict/edits
%We find strong support for including the diploidization rate parameter ($\delta$) in analyses that include only ploidy . %B <- %Rosana, inspect this please. It's a merge of conflicted lines.
% R- I put it up so the line above is not necessary anymore
However, we find only modest support for diploidization in the joint model  (\cref{table:bayesfactors}), and conclusions regarding the relative effects of ploidy and breeding system on diversification are robust to its inclusion.
Furthermore, estimating the rate of diploidization, based on our ploidy level classifications, is highly uncertain (see parameter $\delta$ in \cref{suppfigure:DP,suppfigure:DPAB,suppfigure:IDCDCP,suppfigure:IDCDCPAB}), and yields dramatic changes in ancestral reconstructions (\cref{suppfigure:DPnodipasr,suppfigure:DPasr,suppfigure:DPnodipABasr,suppfigure:DPABasr,suppfigure:IDCDCPnodipasr,suppfigure:IDCDCPasr,suppfigure:IDCDCPnodipABasr,suppfigure:IDCDCPABasr}).

@@

Regardless of whether genome polypoidization, followed by widespread diploidization, is a dominant mechanism of genome evolution in Solanaceae, it is clear that our present understanding of the evolution of ploidy and breeding systems is incomplete.
An increasingly forceful weight of evidence seems to support WGDs in the ancestry of many angiosperms. %cite
It is then easily inferred that many species have undergone diploidization, alongside genome size and chromosome number reductions. %cite
Inference of such a common genome upheaval in eudicot history seems to clash with the data indicating that a homologous mechanism of SI, which breaks down nearly invariably in natural and induced tetraploids \citep{stone_2002,mcclure_2009}, has been present continually in many families, including Solanaceae \citep{igic_2006}. 
Most problematically in this context, it is unclear how to explain the maintenance of trans-generic polymorphism at the orthologous S-loci in this and other families.
As well, chromosome numbers and genome comparisons within the family (esp. `x=12' clade, containing \textit{Solanum} and \textit{Nicotiana}) reveal strong conservation.
\citet{wu_2010a} review the evidence from map-based genome comparisons and find that tomato and potato differ six inversions, tomato and eggplant by 24 inversions and five translocations, tomato and pepper by 19 inversions and six translocations, and tomato and tobacco by ca. 10 inversions and 11 translocations (likely underestimated).
Recovery of such simple relationships would require outstanding convergent loss of duplicated segments.
In either case, all of the approaches make ample assumptions, and it seems that at least some of them will necessitate deep revisions.
Our study, for example, made numerous assumptions in coding trait states (e.g. what constitutes a polyploid or diploid, SI or SC species), in models used for analyses (e.g. irreversibility of SI loss underlain by trans-specific orthologous S-loci), and many more, which could each mislead inference. %B: -> %R: Rosana, take a look at this.
% no discussion of magnitude of \delta vs \rho!
% R- magnitude is not easy to discuss about, what we have are estimates and credible intervals which are completely sample size dependent. With a different sample "magnitude" can change.
% problems: this system has a big set of advantages - carefully curated (co-)occurrences of two traits, genetic basis, etc. and everything is still contradictory and opaque.

@@

Estimating rates of trait linked diversification models is not only a problem of difficult parametric inference (as disscussed in  \citet{rabosky_2010, beaulieu_2015}), but also, a problem of inadequate  ``*SSE'' model specification that can result in misleading inferences when the presence of a second trait has a complex interaction with the focus trait first used to model diversification. 
We presented a roadmap with a series of analyses that can identify whether unknown or unobservable traits are worth pursuing. 
In this roadmap, we have proposed fitting HiSSE models that have effectively shown that some binary states associated with diversification under BiSSE analyses are actually not different in net diversification terms, and instead a hidden state is linked to differences in the diversification rate \citep{beaulieu_2016}.  
If that is the case on a system, raising the question of the identity of the hidden state should be considered as the next step in the modeling process. 
When considering  a second candidate trait, one can model the complex interactions via a MuSSE model, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
Since MuSSE might also suffer from hight type I errors considering more heterogeneity using a hidden state model on top of the multistate diversification model is necessary to adequately infer the effect of the complex interactions in the speciation and extinction process.
% R- new lines
Investigating the process of diversification linked to traits can be done via thorough statistical inferences that carefully evaluate multiple evolutionary histories. 
Background heterogeneity in lineage of diversification is the rule rather than the exception. Inferences that question whether other complex trait interactions are hidden in this background heterogeneity are necessary because they critically contribute to the reconstruction and understanding of diversification.
